---
title: "02_R_Rogramming_Week2"
author: "Andreas Hofheinz"
date: "November 29, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

Function that calclates the mean of a pollutant (sulfate or nitrate) across a specific list of monitors.
The function takes three argumens: 'directory', 'pollunten' and 'id'.
Thereby all NAs are ignored.

```{r test}
pollutantmean <- function(directory, pollutant, id = 1:332){
        
        #Examine if current wd is "specdata"
        curr_wd <- getwd()
        
        if  (substr(curr_wd, nchar(curr_wd)-8+1, nchar(curr_wd)) != "specdata") {
                setwd("specdata")
        }
        
        for (n in id) {print (n)}
                
   
}
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
