---
title: "02_R_Rogramming_Week2"
author: "Andreas Hofheinz"
date: "November 29, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
library(knitr)
opts_knit$set(root.dir = 'C:/Users/andre/OneDrive/Dokumente/01_Programming/Coursera/Data Science Spezialization/02_R-Programming/Week_2')
```

## Exercise 1

Function that calculates the mean of a pollutant (sulfate or nitrate) across a specific list of monitors.
The function takes three argumens: 'directory', 'polluntant' and 'id'.
Thereby all NAs are ignored.

```{r set up, echo=FALSE}
pollutantmean <- function(directory, pollutant, id = 1:332){
        
        new_data <- data.frame()
        mydata <- data.frame()
        curr_wd <- NULL
        
        #Examine if current wd is "specdata"
        curr_wd <- getwd()
        
        if  (substr(curr_wd, nchar(curr_wd)-8+1, nchar(curr_wd)) != directory) {
                setwd(directory)
        }
        
        mydata <- NULL
        for (filenumber in id) {
                #Correction for Filenames, Adding 00 or 0 respectively to id
                if (nchar(filenumber) == 1) {filenumber <- paste0("00",filenumber)} 
                else if (nchar(filenumber) == 2) {filenumber <- paste0("0",filenumber)} 
                myfilename <- paste0(getwd(),"/",filenumber,".csv")
                
                #Read in relevant data and combine them
                new_data <- read.csv(myfilename, header = TRUE)
                mydata <- rbind(mydata,new_data)
        }
                #Calculate mean of pollution and exclude NAs
                pollution_mean <- mean(mydata[,pollutant], na.rm = TRUE)

}
```


```{r set up, echo=FALSE, message=FALSE, warning=FALSE}
test <- pollutantmean(directory = "specdata", pollutant = 'nitrate', id = 30:70)
print(test)
```

## Exercise 2
Write a function that reads a directory full of files and reports the number of completely observed cases in each data file. 
The function should return a data frame where the first column is the name of the file and the second column is the number of complete cases.


```{r set up, echo=FALSE, eval=FALSE}
complete <- function(directory, id = 1:332){
        
        curr_wd <- NULL
        new_data <- data.frame()
        complcases_each_file <- data.frame()
        complcases_new_data <- data.frame()
        
        #Examine if current wd is "specdata"
        curr_wd <- getwd()
        
        if  (substr(curr_wd, nchar(curr_wd)-8+1, nchar(curr_wd)) != directory) {
                setwd(directory)
        }
        
        mydata <- NULL
        for (filenumber in id) {
                
                #Correction for Filenames, Adding 00 or 0 respectively to id
                if (nchar(filenumber) == 1) {filenumber <- paste0("00",filenumber)} 
                else if (nchar(filenumber) == 2) {filenumber <- paste0("0",filenumber)} 
                myfilename <- paste0(getwd(),"/",filenumber,".csv")
                
                #Build dataframe, read new data and add number of complete cases to df mydata
                new_data <- read.csv(myfilename, header = TRUE)
                complcases_new_data[1,1] <- new_data$ID[1]
                complcases_new_data[1,2] <- sum(complete.cases(new_data))
                
                complcases_each_file <- rbind(complcases_each_file,complcases_new_data)
                
                
        }
        names(complcases_each_file) <- c("ID","Nobs")
        complcases_each_file
}





```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
test <- complete(directory = "specdata", id = 3)
print(test)

```







